%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{johnsoncv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage[none]{hyphenat}
\usepackage{multicol}

% Set applicant's personal data for header
\name{Jeffrey Johnson}
% \address{8 South Highview Avenue \linebreak New City, NY 10956}
\address{New City, NY \linebreak www.github.com/jj-28}
\contacts{(845)-269-8744 \linebreak jeffreykjohnsonvb@gmail.com}
\linkedin{www.linkedin.com/in/jeffreyjohnsonswe}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Oswego, NY}{State University of New York (SUNY) College at Oswego}{Fall 2016 – Dec 2020}
			\begin{itemize}
				\item B.A in Computer Science, Dec 2020
				\item Undergraduate Coursework: Programming Languages, Web Services, Data Structures and Algorithms
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Proficient with: Java; Some Experience with: HTML, CSS, JavaScript, Python, C, LaTeX;
				\item Intellij IDEA, Visual Studio Code, Netbeans
				\item Bootstrap 4, Java EE, MySQL, Java Swing 
				\item macOS, Linux (Ubuntu), Windows XP, 7, 8, 10
				\item Microsoft Office, G Suite, Google Ads, Adobe Photoshop CC, Adobe After Effects
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

		% \begin{cvsection}{Employment}
	% 	\begin{cvsubsection}{Technology Instructor}{Lavner Camps}{Summer 2019}
	% 		Engineering Camp with littleBits – Invent And Code (NYU Campus)
	% 		\begin{itemize}
	% 			\item Demonstrated professionalism and adaptability in rapidly changing situations. 
	% 			\item Taught programming syntax and programming methodologies to 9 children weekly.
	% 			\item Implemented engaging activities to encourage teamwork and creativity amongst pupils.
	% 			\item Helped campers create interactive projects with littleBits circuits.
	% 		\end{itemize}
	% 	\end{cvsubsection}
	% \end{cvsection}

	\begin{cvsection}{Selected Coursework}
		
		% \begin{cvsubsection}{Software Engineering (Fall 2017)}{}{}
		% 	GUIGoPiGo
		% 	\begin{itemize}
		% 		\item Designed and implemented a web client for a robot using HTML, CSS, and JavaScript.
		% 		\item Used Git and GitHub to collaborate on code with a 6-person team.
		% 		\item Used Linux terminal to manage files hosted on the robot and run Python code.
		% 		\item Contributed to the Software Requirement Specification document (SRS) that described the goals and purpose of the project.
		% 		\item Created UML diagrams in order to represent the system under development (class, sequence, and activity diagrams).
		% 	\end{itemize}
		% \end{cvsubsection}

		\begin{cvsubsection}{Web Services (Spring 2020)}{}{}
			% Sneakerbeast
			\begin{itemize}
				\item Designed a RESTful API which allowed a person to create an account, add sneakers to a database, and retrieve the information in JSON format.
				\item Implemented the API in multiple frameworks over the course of the semester (Java EE, Servlet API, Grails, Spark Java and Dropwizard).
				\item Utilized Maven to build sources and download dependencies for the project.
			\end{itemize}
		\end{cvsubsection}	

		% \begin{cvsubsection}{Data Structures and Algorithms (Fall 2020)}{}{}
		% 	\begin{itemize}
		% 		\item Created an application that scraps Wikipedia webpages for links, compares them via TD-IDF score and returns the most relevant URL.
		% 		\item Designed a Java Swing GUI that displayed the comparison metrics.
		% 	\end{itemize}
		% \end{cvsubsection}
	

	% \begin{cvsubsection}{Software Quality (Fall 2019)}{}{}
	% 	\begin{itemize}
	% 		\item Worked in a 3 person team to created a Quality Management Plan (QMP) that expressed the team's rationale behind the various testing techniques.
	% 		\item Utilized Specification Based Testing (SBT) techniques to derive equivalence classes.
	% 		\item Derived 100+ test cases for all non-trivial methods and classes in the program.
	% 		\item Implemented all test cases in JUnit and reported a \testbf{96.88\%} Test Suite passing rate.
	% 	\end{itemize}
	% \end{cvsubsection}
	\end{cvsection}



	\begin{cvsection}{Projects}
		\begin{cvsubsection}{JBento (2018- Present)}{}{}
			\begin{itemize}
				\item Created a brand centered around the sale and distribution of Hip-Hop instrumentals.
				\item Ran Google Ads campaigns which resulted in \textbf{38,100} total impressions and \textbf{8,300} YouTube views to increase brand awareness and sales.
				\item Utilizes Adobe After Effects to create dynamic, eye catching visuals.
				\item Utilizes Adobe Photoshop to edit and create images for promotion and social media campaigns.
				\item Researches and implements Search Engine Optimization techniques to improve YouTube video rankings.
				\item Regularly uploads music production content to various social media platforms (Instagram, Twitter, Facebook, YouTube, etc.)
			\end{itemize}
	\end{cvsubsection}
		\begin{cvsubsection}{Other Projects}{}{}
			\begin{itemize}
				\item \textbf{JBento} (2019-Present). Website created to sell instrumental music. Bootstrap 4, HTML, CSS, JavaScript;
				\item \textbf{Turing Machine} (2019). Turing Machine that accepts a “tape” of numbers. Can read and write digits, as well as print to the command line. C;
				\item \textbf{mailMe} (2019). Program that filters source files in a directory and creates a HTML files comprised of all keywords found. Compresses the files and automatically emails them to a user specified email address. Python, Linux, HTML, CSS;
				\item \textbf{Dictionary GUI} (2016). Graphical User Interface for a dictionary comprised of 20,000 words. Java, Java Swing;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Computer Science Association Tutor (2017):} Reinforced object-oriented programming principles and taught useful debugging techniques to students.
				\item \textbf{Digital Music Association President (2018-Present):} Organizes events and workshops focused on music production and showcasing student talent on campus.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}


	\begin{cvsection}{Personal Interests}
		\begin{cvsubsection}{}{}{}	
			\begin{multicols} {2}
			\begin{itemize}
			\setlength\columnsep{4pt}
				\item Music Production (Recording, Composition)
				% \item Instruments (Guitar, Violin, Drums)
								\item Graphic Design

			% \columnbreak
				\item Sneaker Reselling
				\item Basketball

				% \item Mobile Device Repair
			\end{itemize}
			\end{multicols}
		\end{cvsubsection}
	\end{cvsection}
	
	
	
\end{document}
